### 2023-02-28 chapters/conclusion.tex
future work

\begin{itemize}
	\item 
	\textbf{Post-hoc Explainability.} Black-box classifiers are hard to understand and trust, especially in safety-critical domains. We aim to design interpretable classifiers that are explainable by design in this thesis. We can use these classifiers, such as {\imli} and {\crr}, to generate post-hoc explanations for black-box classifiers. Logic-based explanations, such as abductive explanations, Anchor, LORE, CORELS etc., are effective for this purpose. We plan to test how well {\imli} can synthesize explanations with large samples and how well {\crr} can handle more expressive explanations.

>>>>

\begin{itemize}
	\item 
	\textbf{Post-hoc Explainability.} Black-box classifiers are hard to understand and trust, especially in safety-critical domains. In this thesis, we have designed interpretable classifiers that are explainable by design. We can use these classifiers, such as {\imli} and {\crr}, to generate post-hoc explanations for black-box classifiers. In this context, logic-based explanations, such as abductive explanations, Anchor, LORE, CORELS etc., are effective for this purpose. Hence, we plan to test how well {\imli} can synthesize explanations with large samples and how well {\crr} can handle more expressive explanations.
